---
title: "Autonomy-level trade-off (AL0-AL5)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Autonomy-level trade-off (AL0-AL5)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>",
  fig.width = 6, fig.height = 4
)
```

```{r}
library(dynasimR)
sim <- load_example_data()
```

## AL-Efficiency ratio

We trade off KIA reduction versus IHL compliance. The default AL
scenario mapping requires the full MEDTACS-SIM sweep; here we
demonstrate with the two AL points in the shipped example data.

```{r}
al <- al_efficiency(
  sim,
  al_scenarios = c("0" = "M-S00", "1" = "M-S01"),
  ihl_threshold = 0.80,
  n_bootstrap   = 200
)
al$tradeoff_table
```

## Trade-off plot

```{r}
plot_al_tradeoff(al)
```

## Interpretation

The `optimal_al` slot holds the AL level with the highest KIA
reduction while staying above the IHL threshold:

```{r}
al$optimal_al
```

IHL violations (if any):

```{r}
al$ihl_violations
```
