---
title: "Entity flow analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Entity flow analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Many simulations move entities through sequential processing stages
(Stage 1 -> Stage 2 -> Stage 3 -> Stage 4). This vignette shows how
to quantify throughput and identify bottlenecks.

```{r}
library(dynasimR)
sim <- load_example_data()
```

## Stage throughput

```{r}
st <- stage_throughput(sim)
st
```

Only `Stage2` (time_to_stage2) is present in the shipped example,
but the machinery generalises to Stage1..Stage4 when the columns
exist in your simulation output.

## Bottleneck detection

```{r}
detect_bottlenecks(st, threshold = 0.75)
```

## Visualising first-service times

```{r, fig.width = 6, fig.height = 4}
plot_scenario_heatmap(
  sim,
  metrics = c("median_time_to_first_service",
              "median_time_to_stage2")
)
```
