---
title: "Patient flow analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Patient flow analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

The chain of resuscitation moves casualties through Role-1 (point of
injury) to Role-4 (definitive care). This vignette shows how to
quantify throughput and identify bottlenecks.

```{r}
library(dynasimR)
sim <- load_example_data()
```

## Role throughput

```{r}
rt <- role_throughput(sim)
rt
```

Only `Role2` (time_to_role2) is present in the shipped example, but
the machinery generalises to Role1..Role4 when the columns exist in
your simulation output.

## Bottleneck detection

```{r}
detect_bottlenecks(rt, threshold = 0.75)
```

## Visualising first-care times

```{r, fig.width = 6, fig.height = 4}
plot_scenario_heatmap(
  sim,
  metrics = c("median_time_to_first_care",
              "median_time_to_role2")
)
```
